%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %% 
%% LaTeX to get the ``??'' replaced with the number of the last page  %% 
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[12pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactenum will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{enumerate}[#1]}{\end{enumerate}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactenum}[#1]}{\end{compactenum}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Swami Iyer}

\section{Contact Information}
\newlength{\rcollength}\setlength{\rcollength}{1.85in}%
\href{mailto:siyer@cs.umb.edu}{siyer@cs.umb.edu}\\
\href{http://www.swamiiyer.net}{www.swamiiyer.net}

\blankline

\section{Academic Interests}
Evolutionary dynamics on complex networks, machine learning, pedagogy

\blankline

\section{Education}
PhD, Computer Science, University of Massachusetts at Boston, 2013 \\\\
MS, Computer Science, University of Massachusetts at Boston, 2001 \\\\
BE, Electronics and Telecommunication, University of Mumbai, 1996

\blankline

\section{Teaching Experience}
Mathematics Department, University of Massachusetts at Boston
\begin{outerlist}
\item Calculus I (Math 140)
\item Calculus I for Life and Environmental Sciences (Math 145)
\item Calculus II for Life and Environmental Sciences (Math 146)
\item Introduction to Mathematical Biology (Math 303) --- assisted the instructor with the programming sessions
\end{outerlist}

\blankline

Computer Science Department, University of Massachusetts at Boston
\begin{outerlist}
\item Compilers (CS451/651)
\item Intermediate Computing with Data Structures (CS210)
\item Introduction to Computing (CS110)
\item Introduction to Java Part II (CS115L)
\item igniteCS Python Workshop
\end{outerlist}

\blankline

\section{Work Experience}
Senior Lecturer, Computer Science Department, University of Massachusetts at Boston; Sep 2014 -- 
\begin{outerlist}
\item Teach three courses: Introduction to Computing (CS110), Intermediate Computing with Data Structures (CS210), and Compilers (CS451/651)
\item Serve on various department- and college-level committees
\item Conduct research in the areas of evolutionary dynamics on complex networks and machine learning
\end{outerlist} 

\blankline

Lecturer, Computer Science Department, University of Massachusetts at Boston; Sep 2014 -- Aug 2021
\begin{outerlist}
\item Taught three courses: Introduction to Computing (CS110), Intermediate Computing with Data Structures (CS210), and Compilers (CS451/651)
\item Served on various department- and college-level committees
\item Conducted research in the areas of evolutionary dynamics on complex networks and machine learning
\end{outerlist} 

\blankline

Postdoctoral fellow, Physics and Mathematics Departments, University of Massachusetts at Boston; Sep 2013 -- Aug 2014

\begin{outerlist}
\item Worked on computational modeling of the post-transcriptional regulation of PTEN, one of the most commonly lost tumor suppressors in human cancers

\item Taught Calculus 1 (Math 140) and Calculus I and II for Life and Environmental Sciences (Math 145 and Math 146)
\end{outerlist}

\blankline

Software developer, BMC Software, Waltham, MA; Jun 2001 -- May 2006
\begin{outerlist}
\item Designed and developed system- and application-level performance-monitoring software
\end{outerlist}

\blankline

Software developer, Tata Interactive Systems, Bombay, India; Apr 1997 -- Aug 1998

\begin{outerlist}
\item Designed and developed multimedia-rich e-learning software
\end{outerlist}

\blankline

\section{Publications} 
Books

\begin{outerlist}
\item Bill Campbell, Swami Iyer, and Bahar Akbal-Deliba\c{s}. 
\textit{\href{http://www.amazon.com/Introduction-Compiler-Construction-Java-World/dp/1439860882/}{An Introduction to Compiler Construction in a Java World}}. CRC Press (2012). 
\end{outerlist}

\blankline

Papers

\begin{outerlist}
\item Swami Iyer and Timothy Killingback. \textit{Evolution of Cooperation in Social Dilemmas with Assortative Interactions}. Submitted to the Journal of Theoretical Biology.

\item Swami Iyer and Timothy Killingback. \textit{\href{http://dx.doi.org/10.1371/journal.pcbi.1004779}{Evolution of Cooperation in Social Dilemmas on Complex Networks}}. PLoS Computational Biology 12(2), e1004779 (2016).

\item Swami Iyer and Timothy Killingback. \textit{\href{http://dx.doi.org/10.1016/j.jtbi.2016.02.014}{Evolutionary Dynamics of a Smoothed War of Attrition Game}}. Journal of Theoretical Biology 396, 25 -- 41 (2016).

\item Stefanie Gazda, Swami Iyer, Timothy Killingback, Richard Connor, and Solange Brault. \textit{\href{http://dx.doi.org/10.1098/rsos.140263}{Network-based Analysis of Activity Patterns in Bottlenose Dolphins (Tursiops Truncatus) in Cedar Key, Florida}}. Royal Society Open Science 2(3), 140263 (2015).

\item Swami Iyer and Timothy Killingback. \textit{\href{http://dx.doi.org/10.1103/PhysRevE.90.042134}{Evolutionary Dynamics of the Traveler's Dilemma and Minimum Effort Coordination Games on Complex Networks}}. Physical Review E 90(4), 042134 (2014).

\item Swami Iyer, Joshua Reyes, and Timothy Killingback. \textit{\href{http://dx.doi.org/10.1371/journal.pone.0093988}{An Application of Evolutionary Game Theory to Social Dilemmas: The Traveler's Dilemma and the Minimum Effort Coordination Game}}. PLoS ONE 9(4), e93988 (2014).

\item Swami Iyer, Timothy Killingback, Bala Sundaram, and Zhen Wang. \textit{\href{http://dx.doi.org/10.1371/journal.pone.0059613}{Attack Robustness and Centrality of Complex Networks}}. PLoS ONE 8(4), e59613 (2013).

\item Swami Iyer and Dan Simovici. \textit{\href{http://www.swamiiyer.net/publications/multisets_long.pdf}{Structural Classification of XML Documents Using Multisets}}. International Journal on Artificial Intelligence Tools 17(5), 1003 -- 1022 (2008).

\item Swami Iyer and Dan Simovici. \textit{\href{http://www.swamiiyer.net/publications/multisets_short.pdf}{Multisets and Clustering XML Documents}}. Proceedings of the 19th International Conference on Tools with Artificial Intelligence, Patras, Greece (2007). 
\end{outerlist}

\blankline

Poster Presentations

\begin{outerlist}
\item Fateme Pourhasanzade, Swami Iyer, Jesslyn Tjendra, and Selina V\r{a}ge. \textit{\href{https://www.swamiiyer.net/publications/aslo_poster1.pdf}{Individual-based model highlights the importance of trade-offs in shaping bacteria-phage co-evolutionary dynamics}}. Poster presentation at the ASLO Aquatic Sciences Virtual Meeting (2021).

\item Rachel Fiolek, Swami Iyer, and Timothy Killingback. \textit{\href{http://www.swamiiyer.net/publications/evolving_network_poster.pdf}{Complex Network Topologies Resilient to Centrality Attack}}. Poster presentation at the 22nd Annual Massachusetts Statewide Undergraduate Research Conference, University of Massachusetts at Amherst (2016).

\item Swami Iyer, Robert Moray, Prajna Kulkarni, Rahul Kulkarni, and Kourosh Zarringhalam. \textit{\href{http://www.swamiiyer.net/publications/cerna_poster.pdf}{A Machine Learning Approach for Identifying the PTEN Non-coding ceRNA Network}}. Poster presentation at the Winter q-bio Meeting, Waikoloa, Hawaii (2014).

\item Stefanie Gazda, Swami Iyer, Timothy Killingback, Richard Connor, and Solange Brault. \textit{\href{http://www.swamiiyer.net/publications/dolphins_poster2.pdf}{Network Analysis by Activity Reveals Community Overlap and Differences in Centrality of Individuals in Bottlenose Dolphins (Tursiops Truncatus) in Cedar Key, Florida}}. Poster presentation at the 19th Biennial Conference of the 
Biology of Marine Mammals, Tampa, Florida (2011). 

\item Christina Ciarfella, Stefanie Gazda, Swami Iyer, Solange Brault, and Timothy Killingback. \textit{\href{http://www.swamiiyer.net/publications/dolphins_poster1.pdf}{Residency Patterns and Social Structure of Bottlenose Dolphins}}. Poster presentation at the University of Massachusetts at Boston (2010).
\end{outerlist}

\blankline

PhD Thesis

\begin{outerlist}
\item Swami Iyer. \textit{\href{http://scholarworks.umb.edu/doctoral_dissertations/113}{Evolutionary Dynamics on Complex Networks}}. University of Massachusetts at Boston (2013). Advisor: Prof. Timothy Killingback.
\end{outerlist}

\blankline

\section{Awards}
Hjort Scholar Award, Hjort Centre for Marine Ecosystem, Bergen, Norway, 2017 \\\\
Joseph P. Healey Research Grant (Jul 1, 2015-Jun 30, 2016); Role: Co-PI (PI: Timothy Killingback); Grant Title: Evolution of Disease Virulence on Contact Networks; Funds: \$12,000 \\\\
Student Leadership Award, University of Massachusetts at Boston, 2007 \\\\
Outstanding Achievement in Computer Science Award, University of Massachusetts at Boston, 2013

\blankline

\section{Mentoring}
\textit{Graduate Students}
\begin{outerlist}
\item Alexander Zhurkevich. \textit{EFS: An Efficient, Fast and Scalable Semantic Segmentation Pipeline Using TensorFlow 2}. Fall 2021.

\item Jason Held. \textit{A Neural Network Model for Classifying Bubble-based Instructor Evaluations, and an Accompanying Web Portal}. Fall 2017 -- Spring 2018.

\item Jeff Amari, Jason Curran, Divyansh Dhakre, Kinjalk Parmar, Nikhil Sidhwani, and Tory Wheelwright. \textit{Web-based Visualizations of Algorithms}. Fall 2016 -- Spring 2017.

\item Timothy Cronin, Pragna Gopal, Joelle Skaff, and Keith Wright. \textit{Visual MMIX}. Fall 2007 -- Spring 2008.

\item Saaid Baraty, Dhriti Dave, Glenn Hoffman, and Madhavi Tolety. \textit{Visual Parser}. Fall 2002 -- Spring 2003.
\end{outerlist}

\blankline

\textit{Undergraduate Students}

\begin{outerlist}
\item Roy Varon Weinryb. \textit{Detecting Audio with AI}. Summer 2021.

\item Joyce Quach. \textit{Implementation of Algorithms from Introduction to Compiler Construction in a Java World}. Spring 2021.

\item Rachel Fiolek. \textit{Complex Network Topologies Resilient to Centrality Attack}. Fall 2015 -- Spring 2016.

\item Paola Leon Alarcon. \textit{Effect of Vaccination on Epidemic Spread on Complex Networks}. Fall 2015 -- Spring 2016.

\item Kai Ching Lam, Vy Thao Nguyen, Vy Thuy Nguyen, and Matthew H. Santaguida. \textit{Tokanagrammar - A Jigsaw Puzzle for Nerds}. Spring 2013.
\end{outerlist}

\blankline

\section{Service}
\textit{Computer Science Department, University of Massachusetts at Boston}

\begin{outerlist}
\item Curriculum Committee, Fall 2015 --
\item Student Recruitment and Retention Committee, Fall 2015 --
\item Publicity and Outreach Committee, Fall 2016 --
\item Ad-hoc committee to redesign the Apply System (sign-up software for CS lab accounts), Fall 2015 -- Spring 2017
\item Faculty advisor for the Computer Science Club, Spring 2015 -- Spring 2017
\item Student Employment Committee, Fall 2015 -- Spring 2016
\item Ad-hoc committee to switch the language of instruction in CS110 from Java to Python, Spring 2015
\end{outerlist}

\blankline

\textit{College of Science and Mathematics, University of Massachusetts at Boston}

\begin{outerlist}
\item Advising, Counseling, and Supporting Committee, Fall 2021 --
\item GRE (Math section) workshop for McNair fellows, Fall 2019, 2021 
\item CSM Scholarship Committee, Fall 2015 -- Spring 2020
\item Represented the Computer Science department at the Open House event for undergraduates, Fall 2015
\item Represented the Computer Science department at the Welcome Day event for undergraduates, Spring 2015
\end{outerlist}

\end{document}

